---
title: "Performance over trial"
author: "Emily"
date: "2025-03-09"
output: html_document
---

```{r}
pacman::p_load(tidyverse)

# Load simulated data
sim_data <- read.csv("../../data/simulated_data.csv")
# Load Alien data
emp_data <- read.delim("../../data/AlienData.txt", header = T, sep = ",")



```

# Calculate cumulative accuracy. Simulated data 

Tried to calculate and plot the cumulative sum of correct responses.

# Cum_correct: 
We keep track of each correct response per trial.
# Cum_accuracy: 
Calculate the cumulative accuracy (Not sure if this is the right way to do it!).
Divide the current sum of correct responses at the given trial, by trial number, which should give the current correct percentage of responses.

```{r}
# We create two new coloumns to our dataframe
df_sim <- sim_data %>%
  
  mutate(cum_correct = cumsum(correct),
         cum_accuracy = cum_correct / trials)

# Plot cumulative accuracy
ggplot(df_sim, aes(x = trials, y = cum_accuracy)) +
  geom_line(color = "blue", linewidth = 1) +
  labs(
    title = "Simulated data: Cumulative Accuracy Over Trials for GCM agent",
    x = "Trial",
    y = "Cumulative Accuracy"
  ) +
  theme_minimal()



```
# Cummulative accuracy for Alien data - just for funsies


```{r}
# We create two new coloumns to our dataframe like before. 
df_emp <- emp_data %>%
  group_by(subject) %>%  # Group by subject
  mutate(
    cum_correct = cumsum(correct),
    cum_accuracy = cum_correct / row_number() # Row number instead of trial, plot is all weird and wonky if you use trial, but i believe using row_number() should function the same 
  ) %>%



# Plot cumulative accuracy
ggplot(df_emp, aes(x = trial, y = cum_accuracy, color = as.factor(subject))) +
  geom_line() +
  labs(
    title = "Alien data: Cumulative Accuracy Over Trials by Subject",
    x = "Trial",
    y = "Cumulative Accuracy",
    color = "Subject"
  ) +
  theme_minimal()



```


